---
title: "Masters Homework 2"
author: "Jinrong Cheng"
date: "7/21/2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Credit received ##

>- Find summary information about the total blood mercury levels in our NYC HANES data (hint: names(nyc) will call the names of each column). What is the max value, what is the minimum value.  

```{r}
names(nyc)
summary(nyc$MERCURYTOTALBLOOD)
```

>- Bonus/Challenge: What is the Standard Deviation and skewness of the blood mercury?

```{r}
sd(nyc$MERCURYTOTALBLOOD,na.rm = TRUE)
skewness(nyc$MERCURYTOTALBLOOD, na.rm=T)
```



>- Install a package and load, such as "ggplot2" or "dplyr"

```{r}
install.packages("ggplot2")
install.packages("dplyr")
library(ggplot2)
library(dplyr)
```





>- What two commands are needed to install and use a package in R?

```{r}
#install.packages() and library()
```




>- When you read in a .csv file into R, what class is the object that you read in (like nyc)?

 #data.frame

>- What command can you use to determine what type of data is in a column?

```{r}
#class()
```


>- Provide a command to find the type of data in the DX_DBTS column of nyc. 

```{r}
class(nyc$DX_DBTS)
```


>- Provide the same command the type of data but use the other way of indexing from what you did above. 

```{r}
class(nyc[,10])
```



>- What would happen if we had chosen the first 4 columns of NYC HANES and made a matrix? What would the class of the cells in this matrix be? Why?

```{r}
as.matrix (nyc[,1:4])
```


>- If we make a vector,vec<- c(3,9,4,7,8,9), and multiply it by WannaMatrix, what is the value in the third row, third column? 

```{r}
WannaMatrix <- nyc[5:10, 6:9]
WannaMatrix <- as.matrix(WannaMatrix,nrow = 6, ncol = 4)
vec<- c(3,9,4,7,8,9)
wannmultply<- vec*WannaMatrix
wannmultply[3,3]


```



>- What happens if instead we made a vector vec2 <- c(3,9,4,7,8) and multiply it by WannaMatrix, what is the third row, third column value? What is going on? 

```{r}
vec2 <- c(3,9,4,7,8)
wannmultply2<-vec2*WannaMatrix
wannmultply2[3,3]?
```


>- Look up the arguments for read.csv

```{r}
?read.csv
```


>- Use apply() to find the median value of CADMIUM, LEAD CHOLESTEROLTOTAL, GLUCOSESI, CREATININESI, and CREATININE

```{r}
apply(nyc[,c("CADMIUM","LEAD","GLUCOSESI","CREATININESI","CREATININE")], 2,median,na.rm=TRUE)
```


>- Do the same using sapply()

```{r}
sapply(nyc[,c("CADMIUM","LEAD","GLUCOSESI","CREATININESI","CREATININE")],median,na.rm=TRUE)
```

>- Use a for loop to find the median value of columns 16:19

```{r}
for (x in 16:19){
 print(median(nyc[,x],na.rm=TRUE)))
  
}

```


>- Make a for loop to find the standard deviation (hint sd() ) of CHOLESTEROLTOTAL, GLUCOSESI, CREATININESI, AND CREATININE

```{r}
for (x in c("CADMIUM","LEAD","GLUCOSESI","CREATININESI","CREATININE")){
  print(sd(nyc[,x],na.rm=TRUE))
}
```


>- Bonus/Challenge Create a vector in which to put the standard deviations 

```{r}
Sdvector<-NA
for (x in c("CADMIUM","LEAD","GLUCOSESI","CREATININESI","CREATININE")){
  Sdvector<-c(Sdvector,sd(nyc[,x],na.rm=TRUE))
}

```


>- Use ifelse to create a new variable of high and normal A1C dichotomizing with 7 as a threshold for high levels

```{r}

```
###################################################################################OPTIONAL##############################################################################################

>- Subset to only have females (gender == "female")

```{r}

```


>- Create a subset of males and find the median total cholesterol level

```{r}

```


>- Try to create a summary of the mean A1C using two factors, GENDER and DX_DBTS

```{r}

```

Find the class of the first three columns of data. What are they?

```{r}

```


